Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-03-26 RNARedPrint.tex
fix typos

\section*{Funding}
YP is supported
%jointly supported
by the
% French
{\em Agence
  Nationale de la Recherche} and the
%Austrian
Austrian Science Fund (ANR-14-CE34-0011 and FWF-I-1804-N28; project RNALands).  SH is supported by the
German Federal Ministry of Education and Research (BMBF support code
031A538B; de.NBI: German Network for Bioinformatics Infrastructure)
and the
% acknowledged by
%financial support of the
Future and Emerging Technologies programme
% within the Seventh Framework Programme for Research of the
%European Commission, under
(FET-Open grant 323987; project RiboNets).
\revised{The funding bodies did not played any roles in the design
of the study and collection, analysis, and interpretation of data and in writing
the manuscript.}

>>>>

\section*{Funding}
YP is supported
%jointly supported
by the
% French
{\em Agence
  Nationale de la Recherche} and the
%Austrian
Austrian Science Fund (ANR-14-CE34-0011 and FWF-I-1804-N28; project RNALands).  SH is supported by the
German Federal Ministry of Education and Research (BMBF support code
031A538B; de.NBI: German Network for Bioinformatics Infrastructure)
and the
% acknowledged by
%financial support of the
Future and Emerging Technologies programme
% within the Seventh Framework Programme for Research of the
%European Commission, under
(FET-Open grant 323987; project RiboNets).
\revised{The funding bodies did not play any roles in the design
of the study and collection, analysis, and interpretation of data and in writing
the manuscript.}
